Flat-histogram method comparison on 2D Ising Model

### 2020-04-29 ising/ising.tex
updated necessary data and made few corrections in paper.
added figure to paper and improved figure visually.

The WL method can alternatively be implemented as part of a production run which aids in
equilibration~\cite{gross2018massively}. WL is used to generate the weights
resulting in a flat-histogram~\cite{janke2017generalized}. Once a user-defined
minimum $\gamma^{\text{WL}}_t$ is reached, the simulation switches to a final production run
with fixed weights. WL implemented in this way can ensure ergodicity and
detailed balance; however, the convergence of simulation is still impacted by
the choice of the minimum $\gamma^{\text{WL}}_t$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{N32-Cv-error-default.pdf}
  \caption{The maximum error in the heat capacity for each method for the $N=32 \times 32$ and $T_{\min} = 1$ as a function of number of iterations run.  The maximum error is averaged over 8 independent simulations, and the best and worst simulations for each method are shown as a semi-transparent shaded area.}
  \label{fig:N32-cv-error}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{N128-Cv-error-default.pdf}
  \caption{The maximum error in the heat capacity for each method for the $N=128 \times 128$ and $T_{\min} = 1$ as a function of number of iterations run.  The maximum error is averaged over 8 independent simulations, and the best and worst simulations for each method are shown as a semi-transparent shaded area.}
  \label{fig:N128-cv-error}
\end{figure}

@@

\section{Conclusion}
The method performs as well as 1/t-WL and SAD.  Unfortunately, the addition of another tunable parameter Gamma min makes the method somewhat more difficult to implement in practice.

>>>>

The WL method can alternatively be implemented as part of a production run which aids in
equilibration~\cite{gross2018massively}. WL is used to generate the weights
resulting in a flat-histogram~\cite{janke2017generalized}. Once a user-defined
minimum $\gamma^{\text{WL}}_t$ is reached, the simulation switches to a final production run
with fixed weights. WL implemented in this way can ensure ergodicity and
detailed balance; however, the convergence of simulation is still impacted by
the choice of the minimum $\gamma^{\min}_t$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{N32-Cv.pdf}
    \caption{
    The specific heat capacity versus the reciprocal temperature $\beta$ for the $N=32 \times 32$ system for each histogram method.}
    \label{fig:N32-cv}
  \end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{N32-Cv-error-default.pdf}
  \caption{The maximum error in the specific heat capacity for each method for the $N=32 \times 32$ and $T_{\min} = 1$ as a function of number of iterations run.  The maximum error is averaged over 8 independent simulations, and the best and worst simulations for each method are shown as a semi-transparent shaded area.}
  \label{fig:N32-cv-error}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{N128-Cv-error-default.pdf}
  \caption{The maximum error in the specific heat capacity for each method for the $N=128 \times 128$ and $T_{\min} = 1$ as a function of number of iterations run.  The maximum error is averaged over 8 independent simulations, and the best and worst simulations for each method are shown as a semi-transparent shaded area.}
  \label{fig:N128-cv-error}
\end{figure}

@@

\section{Conclusion}
The method performs as well as 1/t-WL and SAD.  Unfortunately, the addition of another tunable parameter $\gamma_{t}^{\min}$ makes the method somewhat more difficult to implement in practice.
